---
title: "Lab 00 - Hello IDS!"
author: "Lucy Zhang"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Michaela", "Nicola", "Jay", 
           "Sherrill", "Crystal"),
  github_username = c("mjoyh", "nicolahan", "jayphilipson", 
                      "Sherri1l", "crystal-suyue"), 
  colour = c("lightpink", "green", "green", 
             "blue", "white"),
  hobby = c("music", "drawing", "knitting", 
            "video game", "shooting game"),
  favourite_number = c(8, 9, 7, 7, 5)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot used bar graph to indicate everyone's favorite color and number through the bar's length and color

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub username", 
          y = "Favorite number between 1-10",
          title = "Self introduction within group")
```

After typing "?labs" into the console, there is a search result indicating it's to "modify axis, legend and plot labels" After I edited the code and knit, the names appeared to be on the x and y axis of the graph

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The bar graph is going to extend forever without tidying the choices since people could have same hobbies, it isn't a concise way to visualize data. I suggest sorting out by data table like excel chart so the axis can coordinate to one cell instead of a bar chart.
